Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-19 paper.tex
[fix] remove m4-macros from code snippets
[add] relations to related work on TEE

%-------------------------------------------------------------------------- sub
\subsection{System and Adversary Model Extensions Supporting TEE}
\label{sec:TEE:advModel}
%
We extend the adversary model of~\cite{Norr21} by allowing the adversary
access to a TEE interface on a party of their choosing before and after the
\mEdhoc{} session.
%
This corresponds to a so-called weak post-compromise security
(PCS)~\cite{DBLP:conf/csfw/Cohn-GordonCG16}.
%

@@

%-------------------------------------------------------------------------- sub
\subsection{Extended Formalism and Security Properties}
\label{sec:TEE:fmAndProps}
Formally, we model the TEE interface by adding two new rewrite rules:
%
\begin{small}
\begin{verbatim}
rule forge_SIG:
   [!LTK_SIG($A, ~ltk), In(xx)] --[TEE($A)]-> [Out(sign(xx, ~ltk))]!>

>>>>

%-------------------------------------------------------------------------- sub
\subsection{System and Adversary Model Extensions Supporting TEE}
\label{sec:TEE:advModel}
%
We extend the adversary model of~\cite{Norr21} by allowing the adversary
access to a TEE interface on a party of their choosing before and after the
\mEdhoc{} session.
%
This allows us to distinguish between a full compromise and a weak one, using
the terminology of~\cite{DBLP:conf/csfw/Cohn-GordonCG16}.
%
A weak compromise is when the adversary have temporary access to the TEE.
%
Seen in the framework of~\cite{DBLP:conf/icics/XuZRWTZ20}, we add adversary
capabilities corresponding to a server adversary, i.e., an adversary that
compromises a party, learns its ephemeral keys and may temporarily access its
TEE, but does not learn the party's long-term key.
%
The model of~\cite{Norr21} only captures server adversary capabilities without
access to the TEE, via the leakage of ephemeral keys, and local adversary
capabilities, or more specifically, a secure-world adversary with read-write
access to the
secure world where the long-term keys reside via the leakage of long-term keys.
%
Our extension allows analysis of so-called weak post-compromise security
(PCS)~\cite{DBLP:conf/csfw/Cohn-GordonCG16}.
%

@@

%-------------------------------------------------------------------------- sub
\subsection{Extended Formalism and Security Properties}
\label{sec:TEE:fmAndProps}
Formally, we model the TEE interface by adding two new rewrite rules:
%
\begin{small}
\begin{verbatim}
rule forge_SIG:
   [!LTK_SIG($A, ~ltk), In(xx)] --[TEE($A)]-> [Out(sign(xx, ~ltk))]
